---
title       : Matrix Exploratory Data Analysis
subtitle    : MEDA
author      : Neurodata
job         : 
framework   : html5slides   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : draft # {standalone, draft}
knit        : slidify::knit2slides #
---

```{r, echo=FALSE, eval=FALSE}
require(slidify)
require(rmarkdown)
render('k15bic.Rmd')
system('open k15bic.html')
#slidify::knit2slides("index.Rmd")
```

```{r,echo=FALSE, eval=FALSE}
bfn <- dir("bic317_size10000/")
node <- gsub("bicK15Raw_", "", bfn)
noe <- gsub("\\.pdf", "", node)

wr <- mapply(function(i,y) paste0("- [", y,"](examples/Kristina15/bic317_size10000/", i, ")  "), bfn, noe)

fileConn <- file("output.txt")
for(i in bfn){
  wr <- paste0("- [stuff](examples/Kristina15/bic317_size10000/", i, ")  ")
  writeLines(wr, fileConn)
}
close(fileConn)
```
# Kristina15 BIC plots

### This set is a run with a sample of size 10000 using various seeds for randomization

#### BIC plots for each non-leaf node (Seed 317, size = 1e4)
- [Node](examples/Kristina15/bic317_size10000/bicK15Raw_Node.pdf)  
- [Node1](examples/Kristina15/bic317_size10000/bicK15Raw_Node1.pdf)  
- [Node11](examples/Kristina15/bic317_size10000/bicK15Raw_Node11.pdf)  
- [Node111](examples/Kristina15/bic317_size10000/bicK15Raw_Node111.pdf)  
- [Node1111](examples/Kristina15/bic317_size10000/bicK15Raw_Node1111.pdf)  
- [Node1112](examples/Kristina15/bic317_size10000/bicK15Raw_Node1112.pdf)  
- [Node112](examples/Kristina15/bic317_size10000/bicK15Raw_Node112.pdf)  
- [Node1121](examples/Kristina15/bic317_size10000/bicK15Raw_Node1121.pdf)  
- [Node1122](examples/Kristina15/bic317_size10000/bicK15Raw_Node1122.pdf)  
- [Node12](examples/Kristina15/bic317_size10000/bicK15Raw_Node12.pdf)  
- [Node121](examples/Kristina15/bic317_size10000/bicK15Raw_Node121.pdf)  
- [Node1211](examples/Kristina15/bic317_size10000/bicK15Raw_Node1211.pdf)  
- [Node1212](examples/Kristina15/bic317_size10000/bicK15Raw_Node1212.pdf)  
- [Node122](examples/Kristina15/bic317_size10000/bicK15Raw_Node122.pdf)  
- [Node1221](examples/Kristina15/bic317_size10000/bicK15Raw_Node1221.pdf)  
- [Node1222](examples/Kristina15/bic317_size10000/bicK15Raw_Node1222.pdf)  
- [Node2](examples/Kristina15/bic317_size10000/bicK15Raw_Node2.pdf)  
- [Node21](examples/Kristina15/bic317_size10000/bicK15Raw_Node21.pdf)  
- [Node211](examples/Kristina15/bic317_size10000/bicK15Raw_Node211.pdf)  
- [Node2111](examples/Kristina15/bic317_size10000/bicK15Raw_Node2111.pdf)  
- [Node2112](examples/Kristina15/bic317_size10000/bicK15Raw_Node2112.pdf)  
- [Node212](examples/Kristina15/bic317_size10000/bicK15Raw_Node212.pdf)  
- [Node2121](examples/Kristina15/bic317_size10000/bicK15Raw_Node2121.pdf)  
- [Node2122](examples/Kristina15/bic317_size10000/bicK15Raw_Node2122.pdf)  
- [Node22](examples/Kristina15/bic317_size10000/bicK15Raw_Node22.pdf)  
- [Node221](examples/Kristina15/bic317_size10000/bicK15Raw_Node221.pdf)  
- [Node2211](examples/Kristina15/bic317_size10000/bicK15Raw_Node2211.pdf)  
- [Node2212](examples/Kristina15/bic317_size10000/bicK15Raw_Node2212.pdf)  
- [Node222](examples/Kristina15/bic317_size10000/bicK15Raw_Node222.pdf)  
- [Node2221](examples/Kristina15/bic317_size10000/bicK15Raw_Node2221.pdf)  
- [Node2222](examples/Kristina15/bic317_size10000/bicK15Raw_Node2222.pdf)  

---
