---
title       : Matrix Exploratory Data Analysis
subtitle    : MEDA
author      : Neurodata
job         : 
framework   : html5slides   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : draft # {standalone, draft}
knit        : slidify::knit2slides #
---

```{r, echo=FALSE, eval=FALSE}
require(slidify)
require(rmarkdown)
setwd("~/neurodata/GH-pages/meda-gh/")
render('weilerbic.Rmd')
system('open weilerbic.html')
#slidify::knit2slides("index.Rmd")
```

```{r,echo=FALSE, eval=FALSE}
bfn <- dir("bic317_size10000/")
node <- gsub("bicWRaw_", "", bfn)
noe <- gsub("\\.pdf", "", node)

wr <- mapply(function(i,y) paste0("- [", y,"](examples/Weiler/bic317_size10000/", i, ")  "), bfn, noe)

FileConn <- file("~/neurodata/GH-pages/meda-gh/examples/Weiler/output.txt")
writeLines(wr, fileConn)
close(fileConn)
system("mvim output.txt")
```
# Weiler BIC plots

### This set is a run with a sample of size 10000 using various seeds for randomization

#### BIC plots for each non-leaf node (Seed 317, size = 1e4)
- [Node](examples/Weiler/bic317_size10000/bicWRaw_Node.pdf)  
- [Node1](examples/Weiler/bic317_size10000/bicWRaw_Node1.pdf)  
- [Node11](examples/Weiler/bic317_size10000/bicWRaw_Node11.pdf)  
- [Node111](examples/Weiler/bic317_size10000/bicWRaw_Node111.pdf)  
- [Node1111](examples/Weiler/bic317_size10000/bicWRaw_Node1111.pdf)  
- [Node1112](examples/Weiler/bic317_size10000/bicWRaw_Node1112.pdf)  
- [Node112](examples/Weiler/bic317_size10000/bicWRaw_Node112.pdf)  
- [Node1121](examples/Weiler/bic317_size10000/bicWRaw_Node1121.pdf)  
- [Node1122](examples/Weiler/bic317_size10000/bicWRaw_Node1122.pdf)  
- [Node12](examples/Weiler/bic317_size10000/bicWRaw_Node12.pdf)  
- [Node121](examples/Weiler/bic317_size10000/bicWRaw_Node121.pdf)  
- [Node1211](examples/Weiler/bic317_size10000/bicWRaw_Node1211.pdf)  
- [Node1212](examples/Weiler/bic317_size10000/bicWRaw_Node1212.pdf)  
- [Node122](examples/Weiler/bic317_size10000/bicWRaw_Node122.pdf)  
- [Node1221](examples/Weiler/bic317_size10000/bicWRaw_Node1221.pdf)  
- [Node2](examples/Weiler/bic317_size10000/bicWRaw_Node2.pdf)  
- [Node21](examples/Weiler/bic317_size10000/bicWRaw_Node21.pdf)  
- [Node211](examples/Weiler/bic317_size10000/bicWRaw_Node211.pdf)  
- [Node2111](examples/Weiler/bic317_size10000/bicWRaw_Node2111.pdf)  
- [Node212](examples/Weiler/bic317_size10000/bicWRaw_Node212.pdf)  
- [Node22](examples/Weiler/bic317_size10000/bicWRaw_Node22.pdf)  
- [Node221](examples/Weiler/bic317_size10000/bicWRaw_Node221.pdf)  
- [Node2211](examples/Weiler/bic317_size10000/bicWRaw_Node2211.pdf)  
- [Node222](examples/Weiler/bic317_size10000/bicWRaw_Node222.pdf)  

---
