---
title: "Matrix Exploratory Data Analysis Output:"
author: "MEDA"
output:
  html_document:
    self_contained: true
    fig_caption: yes
    fig_height: 8
    fig_width: 8
    echo: FALSE
    highlight: pygments
    number_sections: yes
    theme: cerulean
    toc: yes
---

```{r setup, echo = FALSE}
opts_chunk$set(cache=FALSE, echo=FALSE, fig.height = 8, fig.width= 8,
               warning=FALSE, message=FALSE, fig.show='hold',
               comment="#", fig.keep='low', fig.path = outdir)
```

# Structure
## Column types
```{r meda-str1, results = 'hold'}
print(colStr)
```
## Missing values, NAs, and Negatives
```{r meda-str2, results = 'hold'}
print(paste("Are all rows complete?:", complete))
print(paste("Are there any NAs?:", nas))
print(paste("Are any values negative?:", negs))
```

```{r meda-str3, results = 'hold'}
n <- dim(dat)[1]
d <- dim(dat)[2]
if(d <= 12) { print("Structure"); str(dat) }
```

# Level 0

## Heatmap
The heatmap below is a representation of the data with values shown in
color according to magnitude. Mouse hover for column names.

[Heatmap](https://en.wikipedia.org/wiki/Heat_map)

```{r meda-heatmap, fig.h = 12}
tryCatch(p.heat(dat))
```

## First Moment Statistics

The column means and medians are presented in combined 
heatmap and lineplot below.

```{r meda-locations, fig.width = 12}
tryCatch(h1 <- p.location(dat, ccol = colCol))
tryCatch(grid.arrange(h1[[1]], h1[[2]], ncol = 2))
```

# Second Moment Statistics
## Correlation Matrix (heatmap)

The correlation between two random variables is a measure of a specific
type of dependence that involves not only the two variables themselves
but also a random component.  It measures to what degree a linear
relationship exists between then two random variables, where 1 is
corresponds to a direct linear relationship, 0 corresponds to no linear
relationship, and -1 corresponds to an inverse linear relationship.  

1. [Correlation](https://www.encyclopediaofmath.org/index.php/Correlation_(in_statistics))
2. [Correlation and dependence](https://en.wikipedia.org/wiki/Correlation_and_dependence)
3. [Example graphic](https://upload.wikimedia.org/wikipedia/commons/thumb/d/d4/Correlation_examples2.svg/506px-Correlation_examples2.svg.png)

```{r meda-corr}
tryCatch(do.call(corrplot, p.cor(dat, colCol = colCol)))
```

# Density Estimates
## Histogram (1D Heatmaps)

For each feature column, the data are binned and a heatmap is produced
with each bin colored according to count.

```{r meda-1dheat}
tryCatch(p.1dheat(dat, ccol = colCol))
```

## Marginals (2D Heatmaps)
A pairs plot is a popular way of plotting high-dimensional data.  
For every pair of dimensions are plotted showing the specific projection of
the data along those two dimensions. 

For readability a maximum of 8 dimensions are plotted. 

```{r meda-pairs}
tryCatch(p.pairs(dat, maxd = 8))
```

```{r meda-pairsFULL, fig.show='hide', dev='pdf', fig.width = max(8,dim(dat)[2]), fig.height = max(8,dim(dat)[2])}
tryCatch(p.pairs(dat, maxd = Inf))
```

The full plot can be downloaded [here](./meda-pairsFULL-1.pdf)


# Outlier Plots

An outlier is a datapoint that lives relatively far away from the bulk
of other observations. 
Outliers can have unwanted effects on data analysis
and therefore should be considered carefully. 

We use the built-in method from the `randomForest` package in `R`.

1. [randomForest](https://cran.r-project.org/web/packages/randomForest/index.html)
1. [Outlier](https://en.wikipedia.org/wiki/Outlier)
1. [randomForest_outlier](https://www.stat.berkeley.edu/~breiman/RandomForests/cc_home.htm#outliers)

```{r meda-outlier}
if(use.plotly){
  ggplotly(p.try(p.outlier, dat))
} else {
  p.try(p.outlier, dat)
}
```

# Cluster Analysis 

## BIC Plots 
The Bayesian Information Criterion is used to select the model
parameters for Mclust. 

1. [BIC](https://en.wikipedia.org/wiki/Bayesian_information_criterion)
2. [List of mclustModelNames p.88](https://cran.r-project.org/web/packages/mclust/mclust.pdf)

```{r meda-bic}
out <- p.try(p.bic, dat)
```

## Binary Hierarhical GMM Classifications

```{r meda-hmcTree}
#tryCatch(hmcL <- p.hmclust(dat, truth = truth, maxDim = 8))
tryCatch(hmcL <- p.hmc(dat, truth = truth, maxDim = 8, maxDepth = 5,
                       modelNames = modelNames))
```

```{r meda-hmclustFULL, fig.show = "hide", dev = "pdf", fig.height = max(8,dim(dat)[2]), fig.width = max(8,dim(dat)[2])}
  shape <- if(!is.null(truth)){ 
    as.numeric(factor(truth))
  } else {
    20
  }

pairs(dat, 
      pch = shape, 
      col =  hmcL$labels$col, 
      cex = max(min(1.5/log10(dim(dat)[1]), 1.25), 0.05),
      main = "Color is classification; if present, shape is truth"
      )
```

The full plot can be downloaded [here](./meda-hmclustFULL-1.pdf)

## Cluster Dendrogram 

The dendrogram from hierarchical mclust.
The default maxiumum tree depth is set to 4, regardless of BIC.
```{r meda-dendro, fig.height = 5}
tryCatch(p.dend(hmcL))
```

## HMClust output: Stacked Level Cluster means
```{r meda-slcmeans}
tryCatch(pslc <- p.stackM(hmcL, ccol = colCol, centered = center))
print(pslc)
```

## HMClust output: Cluster means
```{r meda-cmeans}
#tryCatch(param <- p.clusterMeans(hmcL$mean, ccol = colCol))
tryCatch(param <- p.clusterMeans(hmcL$means, ccol = colCol, cf = hmcL$ClusterFraction))
#grid.arrange(param[[1]], param[[2]], ncol = 2)
#param[[1]]
param[[2]]
```


## HMClust output: Cluster correlation matrices
```{r meda-ccov, fig.height = 8 +ifelse(dim(hmcL$sigma)[3] %% 2==0,dim(hmcL$sigma)[3]- 2,dim(hmcL$sigma)[3])}
allcor <- abind(hmcL$Get("cor", "level", filterFun = isNotRoot, format = list), along = 3)
tryCatch(p.clusterCov(hmcL$cor, ccol = colCol))
```



# Spectral Analysis

## Cumulative Sum of Variance 

The variance measure how spread out the data are from their mean.
Cumulative variance measures, as a percentage, how much variation 
each dimension contributes to the dataset. 

In this implementation we use principal components analysis to select
linear combinations of the features that explain the dataset best in
low dimensions. 

The plot below shows how much variance is explained when adding columns
one at a time.  The elbows denote good "cut-off" points for dimension
selection. 

1. [Variance](https://www.encyclopediaofmath.org/index.php/Variance)
2. [PCA](https://en.wikipedia.org/wiki/Principal_component_analysis)
3. [Elbows](http://dx.doi.org/10.1016/j.csda.2005.09.010)

```{r meda-cumsum}
if(use.plotly){
  tryCatch(ggplotly(p.try(p.cumvar, dat)))
} else {
  p.try(p.cumvar, dat)
}
```


## Right Singular Vectors Heatmap
The right singular vectors of the data matrix are plotted below in a
heatmap.
```{r meda-rsvH}
tryCatch(rsv <- p.rsv(dat, ccol = colCol, maxd = 8))
rsv[[1]]
```

## Right Singular Vectors Pairs plot
The right singular vectors are plotted below in a pairs plot.
A maximum of 8 pairs will be plotted for readability. 
```{r meda-rsvP}
rsv[[2]]
```

```{r meda-rsvhFULL, fig.show = 'hide', fig.keep='all', dev = 'png', fig.height = max(8, dim(dat)[2]), fig.width = max(8, dim(dat)[2])}
tryCatch(rsvFULL <- p.rsv(dat, ccol = colCol, maxd = Inf))
rsvFULL[[1]]
```
```{r meda-rsvpFULL, fig.show = 'hide', fig.keep='all', dev = 'pdf', fig.height = max(8, dim(dat)[2]), fig.width = max(8, dim(dat)[2])}
rsvFULL[[2]]
```

The full RSV plots can be downloaded [here](./meda-rsvhFULL-1.png)
and [here](./meda-rsvpFULL-1.pdf).

## 3D pca of correlation matrix
```{r meda-3dpca}
try(p.3dpca(dat, colCol = colCol))
```

